---
title: "DEMO"
author: "Pak Yu"
date: "5/4/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

## Loading package

```{r}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(tweenr)
library(gganimate)
library(imager)
library(viridis)
library(plotbb)
library(ggimage)
library(animation)
```

## Loading and Converting the Image of Uterus

extract a subset of pixel coordinate of a image of uterus to use

```{r}

file <- 'data/woman-uterus-line-icon-healthy-internal-organ-vector-30922236.jpg'
im <- load.image(file)
im <- resize(im,round(width(im)*0.75),round(height(im)/0.8))
px <- im < .5
px <- px %>% as.data.frame()
px <- px*-1 
px <- px %>% dplyr::select(x,y)
```

## Loading PC and TSNE Projection Cooridates

```{r}
PC_projection <- read_csv("data/visium/pca_projection.csv")
tsne_cluster <- read_csv("data/visium/clusters.csv") %>% mutate(Cluster=Cluster %>% as.factor)
tsne_projection <- read_csv("data/visium/tsne_projection.csv")
PC_projection <- PC_projection %>% 
                 mutate(across(where(is.numeric), ~ifelse(abs(.x) > 200 ,sample(-100:100, 1),.x))) %>% 
                left_join(tsne_cluster) %>% 
                left_join(tsne_projection)
```

## Backfilling Missing Pixel

```{r}
px_backfill_n <- (dim(PC_projection)-dim(px))[1]
px_backfill <-px[runif(px_backfill_n, 1,dim(PC_projection)[1]) %>% round,]
px <- rbind(px,px_backfill)
```

## Extracting visium Cooridates

```{r}
tissue_positions_list <- read_csv("data/visium/tissue_positions_list.csv", 
                                   col_names = c("Barcode","in_tissue","x","y","x_pixel","y_pixel"), 
                                   col_types = cols(in_tissue = col_logical()))


tissue_positions_list <- tissue_positions_list %>% 
                         dplyr::filter(in_tissue==TRUE) %>% 
                         dplyr::select(-c("x_pixel","y_pixel","in_tissue"))
```

## Random Functions Used in Animation

```{r}
seq_gen <- function(num){ runif(n(),1,4) %>% round %>% factor(.,levels=c(1:4),labels=c("A","C","T","G")) }
val_gen <- function(num){ runif(n(),1,10) %>% ifelse(. >8, .*10,.)}
```

## Making Transition Animation

number of frames can be adjusted by `nframs`. The Dimensions of PC are hard-coded for aesthetic purpose

```{r,warning=FALSE}
start_tween  <- px %>%
                  dplyr::select(x,y) %>%
                  keep_state(20) %>%
                  tween_state(tissue_positions_list %>% select(-Barcode), ease = "cubic-in-out", nframes = 25)%>%
                  keep_state(10) %>%
                  group_split(.frame)
#making random DNA sequencing 
sequcing_tween <- tissue_positions_list %>% mutate(seq=seq_gen(n())) %>% 
                  tween_state(tissue_positions_list %>% mutate(seq=seq_gen(n())), ease = "linear", nframes = 5) %>%
                  tween_state(tissue_positions_list %>% mutate(seq=seq_gen(n())), ease = "linear", nframes = 5) %>%
                  tween_state(tissue_positions_list %>% mutate(seq=seq_gen(n())), ease = "linear", nframes = 5) %>%
                  tween_state(tissue_positions_list %>% mutate(seq=seq_gen(n())), ease = "linear", nframes = 5) %>%
                  tween_state(tissue_positions_list %>% mutate(seq=seq_gen(n())), ease = "linear", nframes = 5) %>%
                  keep_state(10) %>%
                  group_split(.frame)

analysis_tween <- tissue_positions_list %>% mutate(val=val_gen(n())) %>%
                  tween_state(tissue_positions_list %>% mutate(val=val_gen(n())), ease = "linear", nframes = 5) %>%
                  tween_state(tissue_positions_list %>% mutate(val=val_gen(n())), ease = "linear", nframes = 5) %>%
                  tween_state(tissue_positions_list %>% mutate(val=val_gen(n())), ease = "linear", nframes = 5) %>%
                  tween_state(PC_projection %>% dplyr::select(x="PC-1",y="PC-2",Barcode) %>% mutate(val=val_gen(n())),ease = "cubic-in-out", nframes = 20) %>%
                  tween_state(tissue_positions_list %>% mutate(val=val_gen(n())), ease = "linear", nframes = 5) %>%
                  tween_state(tissue_positions_list %>% mutate(val=val_gen(n())), ease = "linear", nframes = 5) %>%
                  tween_state(PC_projection %>% dplyr::select(x="PC-3",y="PC-6",Barcode) %>% mutate(val=val_gen(n())),ease = "cubic-in-out", nframes = 20) %>%
                  tween_state(tissue_positions_list %>% mutate(val=val_gen(n())), ease = "linear", nframes = 5) %>%
                  tween_state(tissue_positions_list %>% mutate(val=val_gen(n())), ease = "linear", nframes = 5) %>%
                  tween_state(PC_projection %>% dplyr::select(x="PC-6",y="PC-2",Barcode) %>% mutate(val=val_gen(n())),ease = "cubic-in-out", nframes = 20) %>%
                  tween_state(tissue_positions_list %>% mutate(val=val_gen(n())), ease = "linear", nframes = 5) %>%
                  tween_state(tissue_positions_list %>% mutate(val=val_gen(n())), ease = "linear", nframes = 5) %>%
                  tween_state(PC_projection %>% dplyr::select(x="PC-9",y="PC-10",Barcode) %>% mutate(val=val_gen(n())),ease = "cubic-in-out", nframes = 20) %>%
                  tween_state(tissue_positions_list %>% mutate(val=val_gen(n())), ease = "linear", nframes = 5) %>%
                  tween_state(tissue_positions_list %>% mutate(val=val_gen(n())), ease = "linear", nframes = 5) %>%
                  tween_state(tissue_positions_list %>% mutate(val=val_gen(n())), ease = "linear", nframes = 5) %>%
                  tween_state(PC_projection %>% dplyr::select(x="TSNE-1",y="TSNE-2",Barcode) %>% mutate(val=val_gen(n())),ease = "quintic-in-out", nframes = 20) %>%
                  tween_state(PC_projection %>% dplyr::select(x="TSNE-1",y="TSNE-2",Barcode) %>% mutate(val=val_gen(n())),ease = "sine-in-out", nframes = 20) %>%
                  tween_state(PC_projection %>% dplyr::select(x="TSNE-1",y="TSNE-2",Barcode) %>% mutate(val=val_gen(n())),ease = "quadratic-in-out", nframes = 20) %>%
                  keep_state(30) %>%
                  group_split(.frame)

tissue_positions_list <- tissue_positions_list %>% inner_join(tsne_cluster)
cluster_tween <- PC_projection %>% dplyr::select(x="TSNE-1",y="TSNE-2",Cluster) %>% mutate(Cluster=as.numeric(Cluster)) %>%
                                                                        mutate(Cluster=case_when(Cluster %% 3 == 0 ~ 0,
                                                                                                 Cluster %% 3 == 1 ~ 1,
                                                                                                 Cluster %% 3 == 2 ~ 2,
                                                                                                 Cluster %% 3 == 3 ~ 3,
                                                                                                 ) %>% as.factor)  %>%
                 keep_state(20) %>% 
                 tween_state(PC_projection %>% dplyr::select(x="TSNE-1",y="TSNE-2",Cluster) %>% mutate(Cluster=as.numeric(Cluster)) %>%
                                                                            mutate(Cluster=case_when(Cluster %% 3 == 0 ~ 2,
                                                                                                     Cluster %% 3 == 1 ~ 3,
                                                                                                     Cluster %% 3 == 2 ~ 1,
                                                                                                     Cluster %% 3 == 3 ~ 0,
                                                                                                     ) %>% as.factor),ease = "cubic-in-out", nframes = 10) %>% 
                 tween_state( PC_projection  %>% dplyr::select(x="TSNE-1",y="TSNE-2",Cluster), ease = "cubic-in-out", nframes = 30) %>%
                 keep_state(20) %>%
                 tween_state(tissue_positions_list %>% dplyr::select(x,y,Cluster),ease = "bounce-in", nframes = 25 ) %>%
                 keep_state(20) %>%
                 tween_state( px %>% mutate(Cluster=tissue_positions_list$Cluster) , nframes= 50, ease = "cubic-in-out" ) %>% 
                 keep_state(50) %>%
                 group_split(.frame)

```

## Building Blank `ggplot` template

```{r}
gg_start <- ggplot() +
        geom_point(
        aes(x = x, y = y),
         show.legend = F) + theme_void() +labs(x="",y="")

gg_seq <- ggplot() +
          geom_text(
            aes(x=x,y=y,color=seq,label=seq)
          ) + 
         theme_void() + 
         guides(color="none") +  
         scale_color_viridis(discrete=TRUE, option="plasma") 
 #+scale_color_manual(values=c("Blue", "Green", "Yellow", "Red"))

gg_analysis <- ggplot() + 
            geom_point( aes(x = x, y = y, color=val,size=val) , show.legend = F) + 
            theme_void() +labs(x="",y="")  + 
            scale_color_viridis(option="plasma")

gg_cluster <- ggplot() +
        geom_point(  aes(x = x, y = y, color=Cluster, shape=Cluster, fill=Cluster), size=4 , show.legend = F) + 
        theme_void() +labs(x="",y="")  +  scale_color_viridis(discrete=TRUE) + 
        scale_shape_manual(values=runif(8,14,25)%>% round) +
        scale_fill_viridis(discrete=TRUE)
```

## Gif Generation

```{r,message=FALSE}
proj_dir <- getwd()
file.path(proj_dir,"data") %>% setwd()
oopt <- ani.options(interval = 1 / 20)
saveGIF({
for (d in start_tween) {
  p <- gg_start %+% d
  plot(p)
}
for( d in sequcing_tween ) {
    p <- gg_seq %+% d
    plot(p)
}
   for(d in analysis_tween){
     p <- gg_analysis %+% d
     plot(p)
   }

   for(d in cluster_tween){
     p <- gg_cluster %+% d
     plot(p)
   }
    }
    ,
    movie.name = "animation.gif",
    ani.width = 360, ani.height = 360)
setwd(proj_dir)
```
